Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-20 Draft.Rmd
Update Draft.Rmd

```{r}
library(tidyverse)
library(tidymodels)
library(broom)
library(carat)
library(randomForest)
library(plotROC)

@@

```{r Bootstrap}
# Create Bootstrap Model
model3 <- nearest_neighbor(neighbors = 5) %>% 
    set_engine("kknn") %>% 
    set_mode("classification")

>>>>

```{r}
library(tidyverse)
library(tidymodels)
library(broom)
library(caret)
library(plotROC)

@@

```{r Bootstrap}
# Create Bootstrap Model (resampling data)
set.seed(123)
model3 <- nearest_neighbor(neighbors = 5) %>% 
    set_engine("kknn") %>% 
    set_mode("classification")
